\documentclass[answers]{exam}
\usepackage[utf8]{inputenc}
\usepackage{color}
\usepackage[document]{ragged2e}
\shadedsolutions

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}

\urlstyle{same}

\title{Dinosaurs\vspace{-2ex}}
\author{Chris \& Hannah\vspace{-2ex}}
\renewcommand{\solutiontitle}{\noindent\textbf{Answer}\par\noindent}
\renewcommand{\thepartno}{Bonus Point}
\renewcommand{\partlabel}{{\addtolength{\leftskip}{20mm} (\thepartno)}}

\begin{document}
\maketitle
\vspace{5mm}

\begin{questions}

    % question 1
    \question The dinosaurs lived during which 3 geological periods?
    
    \begin{parts}
        \bonuspart Can you list the periods in the correct order, from oldest to most recent?
    \end{parts}
    
    \begin{solution}
        \begin{enumerate}
            \item \emph{Triassic}
            \item \emph{Jurassic}
            \item \emph{Cretacious}
        \end{enumerate}
        Source: \href{https://www.nhm.ac.uk/discover/when-did-dinosaurs-live.html?gclid=EAIaIQobChMIgJG-vbzv6QIVlO7tCh12ggzwEAAYASAAEgLPCfD_BwE}{Natural History Museum}
    \end{solution}

    % question 2
    \question Until 2017, a replica skeleton of which breed of dinoasaur was prominently displayed in the Natural History Musem?

    \begin{parts}
        \bonuspart What was it named?
    \end{parts}

    \begin{solution}
        A \emph{Diplodocus} named \emph{Dippy}.
        \linebreak
        Source: \href{https://www.nhm.ac.uk/discover/dippy-the-dino-star.html}{Natural History Museum}
    \end{solution}


    % question 3
    \question Which of the following facts about the \emph{Stegosaurus} is true?
    
    \begin{choices}
        \CorrectChoice They had spikes on their tail, which were used for defence
        \choice They had 15 plates
        \choice Their brain was the size of a walnut
        \choice None of the above
        \choice All of the above
    \end{choices}

    \begin{solution}
        A is true, B and C are false. They had betwen 17 and 22 plates, and their brain was similar in size to a plum.
    \end{solution}

    % question 4
    \question During which geological period did \emph{Tyrannosaurus Rex} live?

    \begin{solution}
        The \emph{Cretacious} period.
    \end{solution}

    % question 5
    \question Steven Spielberg directed the 1993 film \emph{Jurassic Park}, but left much of the post-production to George Lucas so that he could focus on directing which film, released in the same year?

    \begin{solution}
        \emph{Schindler's List}
    \end{solution}

    %question 6
    \question Which of these is \textbf{not} a real dinosaur name?

    \begin{choices}
        \choice Dryosaurus
        \choice Fukuisaurus
        \CorrectChoice Jeffasaurus
        \choice Irritator
        \choice Supersaurus
    \end{choices}

    \begin{solution}
        C - Jeffasaurus
    \end{solution}

    % question 7
    \question What does the term \emph{dinosaur} translate to in common parlance?

    \begin{solution}
        Terrible lizard.
    \end{solution}

    % question 8
    \question What is the name of the earliest known dinosaur?

    \begin{choices}
        \choice Albertosaurus
        \choice Eoraptor
        \choice Nyasasaurus
        \choice Pterosaur
    \end{choices}

    \begin{solution}
        C - Nyasasaurus (known to have existed 231 million years ago)
    \end{solution}

    % question 9
    \question The mass of extinction of dinosaurs was largely due to a meteor impact in Mexico. How many million years ago did this meteor strike occur?

    \begin{parts}
        \bonuspart What is the name of the 150km wide crater left behind by the impact?
    \end{parts}
    \begin{solution}
        66 million years ago (half a point for 65), creating the \emph{Chicxulub} crater.
    \end{solution}


    % question 10
    \question Which of the following ate meat?

    \begin{choices}
        \choice Apatasaurus
        \choice Spinosaurus
        \choice Triceratops
        \choice Stegosaurus
    \end{choices}
    \begin{solution}
        B - Spinosaurus.
    \end{solution}



\end{questions}

\end{document}

