\documentclass[12pt, a4paper]{article}
\usepackage[utf8]{inputenc}
\title{Terms \& Conditions\vspace{-2ex}}}
\author{Dr. Hannah Lunn MRCGP MBChB MA (Oxon)\vspace{-2ex}}
\setlength{\parindent}{0ex}
\setlength{\parskip}{1em}
\renewcommand{\baselinestretch}{1.25}

%% Format section headings
\usepackage{titlesec}
%% Session number followed by title, with smaller font size
\titleformat{\section}
  {\normalfont\fontsize{12}{15}\bfseries}{\thetitle.\quad}{0em}{}
%% Reduce spacing before and after sections
\titlespacing*{\section}{0pt}{0.25\baselineskip}{\baselineskip}

%% Move title up the page
\usepackage[T1]{fontenc}
\usepackage{titling}
\setlength{\droptitle}{-5em}

%% Reference section title as well as number
\usepackage{nameref}

% start of document
\begin{document}
%\begin{titlepage}
\maketitle
%\end{titlepage}

%%%%\section{\fontsize{12}{15}\selectfont Sessions}
\section{Sessions}
\label{sessions}

I would expect a standard session to last 4 hours.
This should breakdown into 3.5 hours of clinical consulting time (which can be face to face appointments, on the day appointments, telephone calls or home visits) and half an hour of administration time.

The minimum time allotted for an appointment should be 10 minutes.

There should be a maximum number of 17 patients per consultation and three ‘catch up’ 10-minute slots staggered throughout the surgery e.g. every 5th or 6th patient.

The half an hour of administration time is for the completion of paperwork generated from the surgery, or to allow for any over-running of the surgery.

If you require me to help with any other paperwork (including correspondence, prescriptions, results) or home visits, the length of standard surgery should be reduced appropriately so that I am able to complete these within the session time.

\section{Booking}

Please specify the type of session to be covered (normal surgery, home visits or on-call).

Please specific the time at which you would like me to arrive at the surgery, and when my session will run from and finish.

\section{Home visits}

A session may include home visits (see \ref{sessions}. \nameref{sessions}).
This should not exceed 2 home visits.
I would expect 30 minutes for home visits, although this may vary between surgeries.

\section{Cancellations}

I will only rarely cancel a booking in the highly unlikely event that I am unable to work (illness, accident, or other significant unforeseen circumstances).

As a GP locum, cancelling my bookings at late notice can result in significant loss of earnings.
I therefore have the following charges with respect to late cancellation of sessions:

\begin{itemize}
  \item 21 days or more in advance of confirmed booking - \textbf{No fee}.
  \item 8 - 20 days in advance of confirmed booking - \textbf{50\% of agreed fee}.
  \item 7 days or less in advance of confirmed booking - \textbf{100\% of agreed fee}.
\end{itemize}

\section{Payment}

I expect to be paid in a timely manner.

I will add a 10\% surcharge to invoices not paid 14 days after the date of invoice.

Pension contributions are not included in the agreed fee.
I will require a signature on a superannuation form for all NHS work.

\end{document}
